Galois Slicing as Differentiation

### 2025-07-11 main.tex
Appendix after references.
Drop 'notes' from title.
[ paper ] some words introducing the main ideas
Start on syntax.
Bump 'categorical framework' to a new section.
Tweaks questions in intro, placeholder for abstract.
Minor reorg of intro.
Start on todo's for new section.
Rename file.
Related work section.
Start on typing rules.
[ tex ] rough attempt to develop the stablity<->differentiable analogy
Defining mu-polynomial functors.
Notation for strength.
Note on grad-CAM.
Add language section.
[ tex ] start on the model construction
Purging section 4.
Anonymise reference to GitHub repo.
Fix Vaka

\documentclass[acmsmall,screen]{acmart}

\usepackage{bbm}
\usepackage{tikz-cd}

\geometry{paperwidth=8.3in, paperheight=11.7in} % force to A4 for now
\settopmatter{printacmref=false}

@@

\title{Approximation as Differentiation notes}

@@

\begin{abstract}
[Abstract]
\end{abstract}
\maketitle

\input{main/introduction}

\pagebreak
\appendix
\input{appendix/notes}

\bibliographystyle{plainnat}
\bibliography{bib}

>>>>

\documentclass[acmsmall,screen,anonymous]{acmart}

\usepackage{tabularx}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{mathpartir}
\usepackage{subcaption}
\usepackage{tikz-cd}
\usepackage{xspace}

%\geometry{paperwidth=8.3in, paperheight=11.7in} % force to A4 for now
\settopmatter{printacmref=false}
\citestyle{acmauthoryear}
\raggedbottom

@@

\title{Galois Slicing as Differentiation}

@@

\begin{abstract}
  \GPS is a technique for program slicing for provenance, developed by
  Perera and collaborators. \GPS aims to explain program executions by
  demonstrating how to track approximations of the input and output
  forwards and backwards along a particular execution. In this paper,
  we explore a analogy between \GPS and differentiable programming,
  seeing the implementation of \GPS as a kind of automatic
  differentiation. Using the CHAD approach to automatic differentation
  due to V{\'a}k{\'a} and collaborators, we reformulate \GPS via a
  categorical semantics. In doing so, we are able to explore
  extensions of the \GPS idea to quantitative interval analysis, and
  to clarify the implicit choices made in existing \GPS
  instantiations.
\end{abstract}
\maketitle

\input{main/introduction}
\input{main/approx-as-tangents}
\input{main/models}
\input{main/language}
\input{main/definability}
\input{main/related-work}
\input{main/conclusion}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bib}

% \pagebreak
% \appendix
% \input{appendix/notes}
